Kepler and the Behemoth: Three Mini-Neptunes in a 40 Million Year Old Association

### 2022-09-06 papers/paper_review/response_1.txt

Sincerely,

Luke Bouma

******************************************
Reviewer #1 MODERATE CONCERNS

REVIEWER COMMENT
----------
Figure 1:
- It is interesting to note that all four planets are concentrated in X-Z, vb-vl*, and vl*-l. This could be because of the small fraction of space that the Kepler field surveyed. Is that accurate? Is there any way to indicated which stars were observed by Kepler in these figures?
- Note that in B&W only the + symbol has a different color than the rest, although since the symbols are different this wasn't much of an issue. The exception is that I can't tell which group is magenta and which lime green, so specifying which are the larger filled circles and which are the smaller would be helpful.
- Why is it important to show the projection of the solar velocity?
RESPONSE
----------
> - The Kepler field is shown in the top panel of the figure, between l of 70 to 85, and b of 5 to 20.  This approximately corresponds to a cone in XYZ -- in case it helps intution, (l,b)=(90,0) corresponds to the line of X=0.  The resulting concentration of the planets in vl* we believe follows from the clustering in l, which is a direct result of the fraction of space that Kepler surveyed, combined with the solar velocity projection effect (described in point three below).
>
> - We have specified in the caption which are the larger and smaller filled circles.
>
> - We have briefly summarized in the first paragraph of section 2.2 why we have shown the projection of the solar velocity: it is because we are interested in how much of the spread in v_l* it might explain.  The short answer is "some of it, but not all of it".  To give a more complete explanation: the Sun moves at ~17 km/s toward (l,b)=(53deg,23deg), relative to a hypothetical circular orbit around the center of the galaxy.  This means that in our observed frame, nearby stars on average appear to move opposite this direction.  At l=53 and 53+180 degrees, the effect does not influence v_l.  At l=53+90 degrees, the effect on v_l is maximized, with amplitude = v_LSR = 17 km/s.  The minimum is at l=53+270 degrees.  Figure 11 of Zari, Brown et al 2018 provides an example for how much of the variance in observed v_l can be ascribed to this projection effect for stars near the galactic plane.  The lower-right panel of our Figure 1 however shows that while the LSR projection accounts for some of the change in observed v_l* in Cep-Her, the data and the gray band do not match!  There therefore needs to be some intrinsic differences in the UVW velocities of these stars (though v_r, v_phi, and v_z is perhaps the better coordinate system).

@@

REVIEWER COMMENT
----------
If at all possible, please assure in Kerr+in prep that the nomenclature does not change such that CH-2 remains CH-2, or update this paper prior to publication.
RESPONSE
----------
> The sub-group identifier will remain the same.

REVIEWER COMMENT
----------
Line 248: I am skeptical of the few % false positive rate (later referenced as 1%). Once stars get hotter than K2, the young and field sequences overlap significantly and so field stars wouldn't likely be outliers in the CAMD. I'm also wondering if not all of the stars are shown on the CAMD; the text states 173 stars in RSG-5; it doesn't quite look to me like there are 173 stars on the upper left panel, but I could be wrong.
RESPONSE
----------
> Thank you for this comment -- it has helped us assess the false positive rates in RSG-5 more closely.
>
> In the color versus absolute magnitude diagram (CAMD), let us use (BP-RP)0 = 1.5 as the dividing line, redward of which stars can be easily seen to be on the pre-main-sequence (or at least elevated relative to typical field stars of the same color).  For RSG-5, there are 89 stars with (BP-RP)0 > 1.5.  One of them falls on the "field star" locus; the others fall on the pre-main-sequence locus.  This implies that, photometrically, 88/89= 98.9% of the candidate RSG-5 members redward of (BP-RP)0=1.5 are photometrically consistent with being on the pre-main-sequence.
>
> Regarding more massive stars, yes, there are plenty: see hr_rsg5.png attached to the response.  The caption of Figure 2 already explicitly states "The range of colors is truncated to emphasize the pre-main-sequence."  The manuscript also has a sentence "Finally, for the plots we set the color range to best visualize the region of maximal age information content: the pre-main-sequence."  But yes, we cannot determine whether these stars more massive than ~K2V are young based on their location in the CAMD.  We can and do use stellar rotation.
>
> Using stellar rotation, we previously wrote in Section 2.3.2 that in RSG-5 41/47 stars have rotation periods consistent with being at least as fast as the Pleiades (87%).  Of the six inconsistent stars, two are the M-dwarfs previously discussed in the text.  The new point that emerged from our reanalysis concerns the other four stars without any detectable rotation period: three of them were the bluest three stars in our sample!  This implies that our blue cutoff was too lenient -- the amplitudes of spot-induced modulation plummet for young stars blueward of the Kraft break (eg. Figure 10 in Rebull+2020, 2020AJ....159..273R).  We have propagated this through the manuscript: we now require (BP-RP)0 > 0.6, and G < 16; the previous cutoff was (BP-RP)0 > 0.5.  The corresponding fraction of RSG-5 stars for which detected rotation periods is 39 detections / 42 expected, i.e. 93%.  
>
> The manuscript has been adjusted following this discussion, including the quantitative statements regarding the pre-main-sequence K and M dwarfs, as well as the rapidly-rotating FGK stars.

REVIEWER COMMENT
----------
Figure 2:
- I don't see any squares for the field sample, is this just the background of small indistinct points?
- Very hard to see Praesepe in black and white
- Praesepe isn't very useful as a reference since the figure is considering things younger than Pleiades. However, it would be useful to see a younger comparison cluster more similar in age to Cep-Her.
RESPONSE
----------
> Yes, the field sample is the gray indistinct background.
>
> We have updated the Praesepe markers to be thicker, which improves their visibility.
>
> The attached figure rotn_ic2602_ic2391_reference.png shows a concatenation from S. Douglas (private communication) of TESS-derived rotation periods from IC-2602 and IC-2391, which are both similar in age to Cep-Her/RSG-5.  These are preliminary rotation period measurements, from the same Douglas+2021 work referenced in the manuscript, which is not yet published.  The IC-2602 and IC-2391 rotation period distributions look quite similar to those from RSG-5, though their work a) extends to lower masses, b) appears to show somewhat more super-Pleiades rotation periods from F5 to G0 spectral types, and c) appears to show more stars on the fast sequence, which are lacking in the RSG-5 sample for unknown reasons.  Given the unpublished nature of this comparison IC-2602 & IC-2391 sample, and the fact that our aim is to simply check for rotational consistency with the stars being at least as young as the Pleiades, we prefer to leave the reference to Douglas+2021 as it is and to not include these data in the manuscript.

@@

REVIEWER COMMENT
----------
Line 280, "Generally speaking, this method is expected": It is not clear that this method of interpolation should be accurate, since it relies on changes occurring linearly in time. Since the ages are quite close to one of the anchors it is probably fine in any case. Please provide a citation or more discussion.
RESPONSE
----------
> We have added the following text: 
> \added{While in reality stellar populations do not evolve linearly in the dimensions of absolute magnitude versus color, in our case the Cep-Her loci are nearly indistinguishable from IC\,2602 (e.g., Figure~3 of \citet{bouma_kep1627_2022}).  Systematic errors incurred in the age from the non-linear evolution are therefore likely much smaller than the $\approx$10\,Myr systematic uncertainty in the absolute reference age for IC\,2602 itself \citep{david_ages_2015,randich_gaiaeso_2018}.

REVIEWER COMMENT
----------
Overall, the discussion of rotation discrepancies in Sec 2.3.2 is not clear and has the feel of the authors trying overly hard to justify their argument (I do agree with the argument, however).
- It would generally be much easier to follow this section if Fig 2 contained a younger cluster for comparison, such as the two cited at the end of this section.
- After some reflection, I think the argument about the M dwarfs is that both very young M dwarfs still in the process of contracting, and moderately young M dwarfs that have just begun to spin down, can have periods of 10-12 days. I suggest simply stating this up front, and then only consider FGK stars in the subsequent discussion.
- Line 328: "no field star outliers" - but the authors have previously stated that there is one outlier.
- 13% seems like a lot of pole-on stars for random chance, and at these young ages the amplitudes should almost always be quite large. Rampalli+2021 detects a higher fraction of rotators amongst older Praesepe stars. It seems more likely that the false positive rate is similar to the other sub-associations considered.
RESPONSE
----------
> - Regarding younger clusters for comparison, please see our response regarding Figure 2, which contains the comparison against IC-2391 and IC-2602, and our reasons for not including it in the manuscript.
>
> - Regarding M dwarfs, the suggestion to exclude them by cutting at say (BP-RP)0=1.84 (Mamajek's M0V main sequence boundary) would have the following effect.  In RSG-5, it would omit 13 stars currently in the 42 star sample, including the one non-detection, and the one 12.7 day rotator.  The net result would be that 28 stars in RSG-5 would have rotation period detections consistent with being younger than the Pleaides, out of 29 expected.  In CH-2, this cut would omit 10 stars currently in the 19 star sample.  The net result would be that 8 stars in CH-2 would have rotation period detections consistent with being younger than the Pleiades, out of 9 stars expected.   We would prefer to not make this cut, chiefly because of the factor of 2x reduction in the CH-2 rotation sample, which would weaken its statistical power.  In our view, the rotation periods of the early M-dwarfs are still informative, particularly in the sense that non-detections would imply inconsistency with the expected >1% amplitude spot-induced modulations (e.g. Figure 10 of Rebull 2020 2020AJ....159..273R).  We have clarified the wording in the relevant paragraphs of Section 2.3.2 to emphasize the main points, which concern the range of plausible false positive rates based on the rotation period analysis.  The contamination rates seem to be at most one in three for CH-2 candidate members, and one in fifteen for candidate RSG-5 members.
>
> - Regarding "nearly no field star outliers", which was the relevant phrase, the wording has been adjusted to "only one field star outlier".
>
> - Regarding 87/13%, please see the earlier discussion regarding the sensitivity of this fraction to our blue cutoff boundary, and the adjustment to (BP-RP)0 > 0.6, which yielded a 93% detection rate.  Given the small amplitudes of rotation-induced signals in the bluer regime, this seems like the wiser approach.  Based on the color absolute magnitude diagrams, the false positive rate in the candidate RSG-5 members is quite likely lower than in the candidate δ Lyr or CH-2 members.

REVIEWER COMMENT
----------
The discussion of vsini measurements did not provide adequate details, such as macroturbulence and potential impact of the targets being very young.
RESPONSE
----------
> We have added the following footnote to the manuscript:
>
> \footnote{The broadening is calculated using the joint rotational and macroturbulent broadening kernel from \citet{hirano_2011}, assuming that the macroturbulent velocity scales with effective temperature similar to the prescription from \citet{2014MNRAS.444.3592D}.  The latter assumption could be a source of systematic uncertainty in our equatorial velocity measurements, since the macroturbulent velocity could be systematically higher (or lower) on the pre-main-sequence than it is for more slowly rotating field stars.}
>
> We have also corrected the number of significant figures in the KOI-7368 vsini, and imposed an uncertainty floor of 1 km/s.

### 2022-09-06 papers/paper/ms.tex
update response

Figure~\ref{fig:age} also shows that most RSG-5 and CH-2 members
overlap with the $\delta$~Lyr cluster, and that the groups are
therefore roughly the same age.  To quantify this, we use the method
introduced by \citet[][their Section~6.3]{gagne_mutau_2020}.  The idea
is to fit the pre-main-sequence loci of a set of reference clusters,
and to then model the locus of the target cluster as a linear
combination of these reference cluster loci.  For our reference
clusters, we used UCL, IC\,2602, and the Pleiades, with the
memberships reported by \citet{Damiani2019} and
\cite{CantatGaudin2018a} respectively.  We adopted ages of 16\,Myr for
UCL \citep{pecaut_star_2016}, 38\,Myr for IC\,2602
\citep{david_ages_2015,randich_gaiaeso_2018} and 112\,Myr for the
Pleiades \citep{dahm_2015}.  These assumptions and the subsequent
processing steps taken to exclude field stars and binaries were
identical to those described in \citet{bouma_kep1627_2022}.  The mean
and uncertainty of the resulting age posterior are $46^{+9}_{-7}$\,Myr
for RSG-5, and $36^{+10}_{-8}$\,Myr for CH-2.  For comparison, this
procedure yields an age for the $\delta$~Lyr cluster of
$38^{+6}_{-5}$\,Myr.  The older isochronal age of RSG-5 is consistent
with its location relative to the $\delta$~Lyr cluster in the upper
left panel of Figure~\ref{fig:age}.
Generally speaking, this method is expected to be accurate provided
that the metallicities of IC\,2602 and the Cep-Her groups (RSG-5,
CH-2, and the $\delta$~Lyr cluster) are roughly identical.  The
spectroscopic metallicities that we find in Section~\ref{sec:stars}
suggest that this is indeed the case.
\added{While in reality stellar populations do not evolve linearly in
the dimensions of absolute magnitude versus color, in our case the
Cep-Her loci are nearly indistinguishable from IC\,2602 (e.g.,
Figure~3 of \citet{bouma_kep1627_2022}).  Systematic errors incurred
in the age from the non-linear evolution are therefore likely much
smaller than the $\approx$10\,Myr systematic uncertainty in the
absolute reference age for IC\,2602 itself
\citep{david_ages_2015,randich_gaiaeso_2018}.

@@

\paragraph{Spectra}
For Kepler-1643, we acquired two iodine-free spectra from Keck/HIRES
on the nights of 2020 Aug 16 and 2021 Oct 25.  The acquisition and
analysis followed the usual techniques of the California Planet Survey
\citep{howard_cps_2010}.  We derived the stellar parameters ($T_{\rm
eff}, \log g, R_\star$) using \texttt{SpecMatch-Emp}
\citep{yee_SM_2017}, which yielded values in $<$$1$-$\sigma$ agreement
with those from the cluster-isochrone method.  This approach also
yielded $[{\rm Fe/H}]=0.13 \pm 0.09$.  Using the broadened synthetic
templates from \texttt{SpecMatch-Synth} \citep{petigura_cksi_2017}, we
found $v\sin i = 9.3 \pm 1.0\,\mkms$.  The systemic radial velocity at
the two epochs was $-9.1 \pm 1.9\,\mkms$ and $-7.8\pm 1.2\,\mkms$
respectively \citep{chubak_2012}.  To infer the equivalent width of
the \ion{Li}{1} 6708\,\AA\ doublet, we followed the procedure
described by \citet{bouma_2021_ngc2516}.  This yielded a strong
detection: ${\rm EW}_{\rm Li} = 130^{+6}_{-5}$\,m\AA, with values
consistent at $<$$1$-$\sigma$ between the two epochs.   The quoted
value does not correct for the \ion{Fe}{1} blend at 6707.44\,\AA.  Given the purported age and
effective temperature of the star, the lithium equivalent width is
somewhat low.  We discuss this in greater depth in
Section~\ref{subsec:specyouth}.

@@

\subsection{KOI-7368}
\paragraph{Spectra}
For KOI-7368, we acquired a spectrum on 2015 June 1 using the echelle
spectrograph (TRES; \citealt{furesz_tres_2008}) mounted at the
Tillinghast 1.5m at the Fred Lawrence Whipple Observatory.  The
Stellar Parameter Classification pipeline for TRES has been described
by \citet{2021tsc2.confE.124B}.  It is based on the synthetic template
library constructed by \citet{Buchhave2012}.  The resulting stellar
parameters ($T_{\rm eff}, \log g, R_\star$) agreed with those from the
cluster-isochrone method within $1$-$\sigma$.  Auxiliary
spectroscopic parameters included the metallicity $[{\rm Fe/H}]= -0.02
\pm 0.08$, the equatorial velocity $v\sin i = 20.21 \pm 0.50\,\mkms$,
and the systemic velocity ${\rm RV}_{\rm sys} = -10.9 \pm 0.2\,\mkms$.
The Li 6708\AA\ EW measurement procedure yielded ${\rm EW}_{\rm Li} =
236^{+16}_{-14}$\,m\AA.

>>>>

Figure~\ref{fig:age} also shows that most RSG-5 and CH-2 members
overlap with the $\delta$~Lyr cluster, and that the groups are
therefore roughly the same age.  To quantify this, we use the method
introduced by \citet[][their Section~6.3]{gagne_mutau_2020}.  The idea
is to fit the pre-main-sequence loci of a set of reference clusters,
and to then model the locus of the target cluster as a linear
combination of these reference cluster loci.  For our reference
clusters, we used UCL, IC\,2602, and the Pleiades, with the
memberships reported by \citet{Damiani2019} and
\cite{CantatGaudin2018a} respectively.  We adopted ages of 16\,Myr for
UCL \citep{pecaut_star_2016}, 38\,Myr for IC\,2602
\citep{david_ages_2015,randich_gaiaeso_2018} and 112\,Myr for the
Pleiades \citep{dahm_2015}.  These assumptions and the subsequent
processing steps taken to exclude field stars and binaries were
identical to those described in \citet{bouma_kep1627_2022}.  The mean
and uncertainty of the resulting age posterior are $46^{+9}_{-7}$\,Myr
for RSG-5, and $36^{+10}_{-8}$\,Myr for CH-2.  For comparison, this
procedure yields an age for the $\delta$~Lyr cluster of
$38^{+6}_{-5}$\,Myr.  The older isochronal age of RSG-5 is consistent
with its location relative to the $\delta$~Lyr cluster in the upper
left panel of Figure~\ref{fig:age}.
Generally speaking, this method is expected to be accurate provided
that the metallicities of IC\,2602 and the Cep-Her groups (RSG-5,
CH-2, and the $\delta$~Lyr cluster) are roughly identical.  The
spectroscopic metallicities that we find in Section~\ref{sec:stars}
suggest that this is indeed the case.
\added{While in reality stellar populations do not evolve linearly in
the dimensions of absolute magnitude versus color, in our case the
Cep-Her loci are nearly indistinguishable from IC\,2602 (e.g.,
Figure~3 of \citet{bouma_kep1627_2022}).  Systematic errors incurred
in the age from the non-linear evolution are therefore likely much
smaller than the $\approx$10\,Myr systematic uncertainty in the
absolute reference age for IC\,2602 itself
\citep{david_ages_2015,randich_gaiaeso_2018}.}

@@

\paragraph{Spectra}
For Kepler-1643, we acquired two iodine-free spectra from Keck/HIRES
on the nights of 2020 Aug 16 and 2021 Oct 25.  The acquisition and
analysis followed the usual techniques of the California Planet Survey
\citep{howard_cps_2010}.  We derived the stellar parameters ($T_{\rm
eff}, \log g, R_\star$) using \texttt{SpecMatch-Emp}
\citep{yee_SM_2017}, which yielded values in $<$$1$-$\sigma$ agreement
with those from the cluster-isochrone method.  This approach also
yielded $[{\rm Fe/H}]=0.13 \pm 0.09$.  Using the broadened synthetic
templates\added{\footnote{The broadening is calculated using the joint
rotational and macroturbulent broadening kernel from \citet{hirano_2011},
assuming that the macroturbulent velocity scales with effective temperature similar
to the prescription from \citet{2014MNRAS.444.3592D}.  The latter assumption could be a 
source of systematic uncertainty in our equatorial velocity measurements, since
the macroturbulent velocity could be systematically higher (or lower) on
the pre-main-sequence than it is for more slowly rotating field stars.}}
 from \texttt{SpecMatch-Synth} \citep{petigura_cksi_2017}, we
found $v\sin i = 9.3 \pm 1.0\,\mkms$.  The systemic radial velocity at
the two epochs was $-9.1 \pm 1.9\,\mkms$ and $-7.8\pm 1.2\,\mkms$
respectively \citep{chubak_2012}.  To infer the equivalent width of
the \ion{Li}{1} 6708\,\AA\ doublet, we followed the procedure
described by \citet{bouma_2021_ngc2516}.  This yielded a strong
detection: ${\rm EW}_{\rm Li} = 130^{+6}_{-5}$\,m\AA, with values
consistent at $<$$1$-$\sigma$ between the two epochs.   The quoted
value does not correct for the \ion{Fe}{1} blend at 6707.44\,\AA.  Given the purported age and
effective temperature of the star, the lithium equivalent width is
somewhat low.  We discuss this in greater depth in
Section~\ref{subsec:specyouth}.

@@

\subsection{KOI-7368}
\paragraph{Spectra}
For KOI-7368, we acquired a spectrum on 2015 June 1 using the echelle
spectrograph (TRES; \citealt{furesz_tres_2008}) mounted at the
Tillinghast 1.5m at the Fred Lawrence Whipple Observatory.  The
Stellar Parameter Classification pipeline for TRES has been described
by \citet{2021tsc2.confE.124B}.  It is based on the synthetic template
library constructed by \citet{Buchhave2012}.  The resulting stellar
parameters ($T_{\rm eff}, \log g, R_\star$) agreed with those from the
cluster-isochrone method within $1$-$\sigma$.  Auxiliary
spectroscopic parameters included the metallicity $[{\rm Fe/H}]= -0.02
\pm 0.08$, the equatorial velocity \replaced{$v\sin i = 20.21 \pm 0.50\,\mkms$}{$v\sin i = 20.2 \pm 1.0\,\mkms$},
and the systemic velocity ${\rm RV}_{\rm sys} = -10.9 \pm 0.2\,\mkms$.
The Li 6708\AA\ EW measurement procedure yielded ${\rm EW}_{\rm Li} =
236^{+16}_{-14}$\,m\AA.
